MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
updated attack and bib

\textbf{Numeric Comparison}: a 6 digit number is displayed on both devices and a user confirms that the numbers match (this is designed for devices that both have display and input capabilities)\\\\
\textbf{Passkey Entry}: designed when one device has input (keyboard) and the other mostly display; the device that has the display shows a 6 digit number, which the user types in on the input device.\\\\
\textbf{Just Works}: one device has no input or display; the user must accept the connection without being able to visualize that the numbers are the same (more in nist)\\\\
\textbf{Out of Band (OOB)}: designed to connect when two devices are touched together, (e.g. Near Field Communication or NFC)\\\\
%TODO 5 steps of pairing protocol

\subsection{MITM Bluetooth Attacks}
We focus on man-in-the-middle attacks (MITM) against devices that use Passkey Entry as their primary mode of authentication for pairing. Historically, these attacks have been simple to implement and successful using a variety of approaches.

@@

\section{Attack Overview}
There are 4 main steps to executing the attack:
\begin{enumerate}
\item Find Bluetooth Address of the keyboard
\item Execute DoS attack against victim
\item Pair with keyboard and victim
\item Forward keystrokes to victim
\end{enumerate}
TODO 
\subsection{Finding the Keyboard Bluetooth Address}
The work relies on the assumption that we can find the MAC address of the keyboard easily and quickly using a Bluetooth sniffer and packet capturing software such as Kismet[link]. Although it is possible to manually program a Bluetooth card, it is possible to obtain hardware that sniffs and integrates with Kismet. Project Ubertooth provides both hardware and a plugin for Kismet that allows you to promiscuously sniff Bluetooth packets and displays the MAC address from whatever device is sending out the packets.

>>>>

\textbf{Numeric Comparison}: a 6 digit number is displayed on both devices and a user confirms that the numbers match (this is designed for devices that both have display and input capabilities)\\\\
\textbf{Passkey Entry}: designed when one device has input (keyboard) and the other mostly display; the device that has the display shows a 6 digit number, which the user types in on the input device.\\\\
\textbf{Just Works}: one device has no input or display; the user must accept the connection without being able to visualize that the numbers are the same (more in nist)\\\\
\textbf{Out of Band (OOB)}: designed to connect when two devices are touched together, (e.g. Near Field Communication or NFC)\\\\
%TODO 5 steps of pairing protocol
\subsection{MITM Bluetooth Attacks}
We focus on man-in-the-middle attacks (MITM) against devices that use Passkey Entry as their primary mode of authentication for pairing. Historically, these attacks have been simple to implement and successful using a variety of approaches.

@@

\section{Attack Overview}
Based on prior research, the theoretical attack would take 4 main steps to executing the attack, which are as follow:
\begin{enumerate}
\item Find Bluetooth Address of the keyboard
\item Execute DoS attack against victim
\item Pair with keyboard and victim
\item Forward keystrokes to victim
\end{enumerate}

Each step is outlined in detail in the following subsections.

\subsection{Finding the Keyboard Bluetooth Address}
The work relies on the assumption that we can find the Bluetooth address of the keyboard easily and quickly using a Bluetooth sniffer and packet capturing software such as Kismet\cite{kismet}. Although it is possible to manually program a Bluetooth card, it is possible to obtain hardware that sniffs and integrates with Kismet. Project Ubertooth provides both hardware and a plugin for Kismet that allows you to promiscuously sniff Bluetooth packets and displays the Bluetooth address from whatever device is sending out the packets.
